---
title: "GRAPHS"
output: 
  html_document:
    theme: united
    toc: TRUE
    toc_float: TRUE
params:
  RES_ageband_by_gender: NULL
  RES_ageband: NULL
  RES_gender: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r params_start}
# ```{css}
# h1 {color: #ed008c}
# h2 {color: #00adef}
# h3 {color: #6ccff6}
# .list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {background-color: #00adef; border-color: #00adef}
```



```{r params}
RES_gender=params$RES_gender
RES_ageband=params$RES_ageband
RES_ageband_by_gender=params$RES_ageband_by_gender
```

# COUNTS BY GENDER
```{r graph1}
graph1<-ggplot(RES_gender,aes(year,N,fill=gender))+
  geom_col(position = "dodge2")+
  theme_hc()

ggplotly(graph1)
```

# COUNTS BY AGE
```{r graph2}
graph2<-ggplot(RES_ageband,aes(year,N,fill=age_bands))+
  geom_col(position = "dodge2")+
  theme_hc()

ggplotly(graph2)

```

# COUNTS BY AGE AND GENDER
```{r graph3}
graph3<-ggplot(RES_ageband_by_gender,aes(year,perc,fill=age_bands))+
  geom_col()+
  facet_grid(~gender)+
  theme_hc()

ggplotly(graph3)
```